Marginally-Stable Thermal Equilibria of Rayleigh-Bénard Convection

### 2021-05-26 publication_materials/ms_rbc.tex

The MSTE retain several key features that are prevalent in experiments and simulations: $\Nu \sim\Ra^{1/3}$ scaling, large-scale convective cell structures, and minimum length scale agreement. 
They also exhibit unique and unexpected features: mean temperature gradient-reversals/dips, high kinetic energy flows, and a larger $\Nu$ than other time-invariant solutions. 
When initializing with different mean temperature profiles, we find the same MSTE, suggesting these equilibria might be unique.

@@

@@

\section*{Acknowledgments}
The authors thank Geoff Vasil, Greg Chini, Kyle Augustson, and Emma Kaufman for their valuable feedback and suggestions. 
We also thank the \texttt{Dedalus} and \texttt{Eigentools} development teams. 
Computations were conducted with support by the NASA High End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades with allocation GIDs s2276.

>>>>

The MSTE contain large-scale convective cell structures, and have $\Nu\sim\Ra^{1/3}$.
These are similar to what has been found in experiments and direct numerical simulations.
But MSTE also exhibit unique and unexpected features: mean temperature gradient-reversals/dips, high kinetic energy flows, and a larger $\Nu$ than other time-invariant solutions. 
When initializing with different mean temperature profiles, we find the same MSTE, suggesting these equilibria might be unique.

@@

Another significant difference with DNS is the treatment of shear in the boundary layers.
At sufficiently high $\Ra$, the shear in the kinetic boundary layers could become unstable and turbulent \cite{Ahlers}.
This cannot occur in our quasilinear model because the background state has no velocity shear.
One avenue for future work is to include a mean horizontal flow, which could develop boundary layer structures.
In that case, we would search for states which also balance viscous and Reynolds stresses across the domain.
Perturbations about this background state could include shear flow instabilities.
Another approach would be to use the generalized quasilinear approximation, in which the background state includes both the mean and low-wavenumber temperature and velocity profiles \cite{marston2016}.
This would allow for linear instabilities of the shear driven by low-wavenumber rolls, as we see in all MSTE.
Generalized quasilinear calculations are inherently multi-dimensional, so they are more computationally expensive than the eigenvalue-based analysis used to find MSTE.
Despite these limitations, our one-dimensional MSTE states capture many interesting features of convection.

@@

\section*{Acknowledgments}
This paper is dedicated to Charlie Doering, who greatly influenced the way many of us think about Rayleigh-Benard convection.
DL met Charlie as a WHOI GFD summer fellow, and has difficulty imagining Walsh Cottage without Charlie's friendly and open scientific style, and enthusiasm for softball.
The authors thank Geoff Vasil, Greg Chini, Kyle Augustson, and Emma Kaufman for their valuable feedback and suggestions.
We would also like to thank Charlie Doering and Baole Wen for the tabulated DNS and ECS data for figure~\ref{fig:nu_vs_ra}.
We thank the \texttt{Dedalus} and \texttt{Eigentools} development teams. 
Computations were conducted with support by the NASA High End Computing (HEC) Program through the NASA Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades with allocation GIDs s2276.
